### 2024-03-04 ms.qmd
Update ms.qmd

```{r, coeficients}
#| label: coeficients
# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
# And critical value:
critical_value <- qnorm((1 + 0.95) / 2)
## A) L. delicata
#### A.1.- CORT
mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
#
deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
#
#### A.2.- Temperature
mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
#
deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
#
#### A.3.- Interaction

>>>>

```{r, coefficients}
#| label: coeficients
# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
# And critical value:
critical_value <- qnorm((1 + 0.95) / 2)
## A) L. delicata
#### A.1.- CORT
mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
#
deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
#
#### A.2.- Temperature
mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
#
deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
#
#### A.3.- Interaction
